Methods with preconditioning with weight decay regularization

### 2023-03-10 paper/main.tex
add new weight decay and graphics

\section{Introduction}
In machine learning we consider optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression. This minimization problem can be difficult to solve, particularly when the number of training
samples n, or problem dimension d, is large, or if the problem is nonconvex.

There are second order preconditioners methods for solving this problem, such as Adam, OASIS, AdaHessian.

>>>>

\section{Introduction}
In machine learning we consider unconstrained optimization problem
\begin{equation*}
	\min_{w \in \mathbb{R}^d} f(w)
\end{equation*}
Problems of the form (1) cover a plethora of applications, including empirical risk minimization,
deep learning, and supervised learning tasks such as regularized least squares or logistic regression. This minimization problem can be difficult to solve, particularly when the number of training
samples n, or problem dimension d, is large, or if the problem is nonconvex.

There are second order preconditioners methods for solving this problem, such as Adam \citep{kingma2014adam} , OASIS \citep{}, AdaHessian.
